NLIZE: A Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models

### 2018-03-27 paper/application.tex
minor fixeds

\section{Put it All Together}

\label{sec:caseStudy}

In this section, we utilizes the perturbation based analysis
to illustrate how the proposed system can be used
to diagnose the model behavior, study the model's attention mechanism.

\subsection{Where Are the Mistakes?}

\subsection{How Attention Affect the Prediction?}

% \subsection{Is Attention All You Need?}

>>>>

\section{Application Scenarios}
\label{sec:caseStudy}
% \shusen{A full case study that driven by the visualization task and the question associated with them}
In this section, we discuss application scenarios, in which the domain experts utilize the perturbation driven analysis to explore and assess the model and interpret the attention mechanism.
%
These scenarios are summarized by the domain experts who integrated the tool into their model exploration workflow.

\subsection{Scenario 1: Interpretting Model Decision Making Process}
The three stages (encoder, attention, classifier) of the model work in synergy to produce the correct prediction.
% \shusen{difference in sensitivity among entail natural and contradict relationships}
% the generate the correct prediction for the wrong reason

\subsection{Scenario 2: Which Part of the Model is the Problem?}

\subsection{Scenario 3: Handcraft Example Exploration}
Well-know tough examples, such as the Facebook IPO example discussed in Section~\ref{sec:background}.

\subsection{Scenario 4: Handcraft Example Exploration?}

%\subsection{Is the Prediction Stable?}
%\subsection{Where Are the Mistakes?}
%\subsection{How Attention Affect the Prediction?}
%\subsection{What Does It Take to Change the Prediction?}
%\subsection{Is Attention All You Need?}
